Rhesus macaque drug study

### 2021-05-19 macaque/macaque_DE.Rmd
initial commit

# get and combine signatures
df_signatures = lapply( colnames(coef(fit))[-1], function(drug){
  tab = topTable(fit, coef=drug, sort.by="none", number=Inf)[,'logFC', drop=FALSE]
  colnames(tab) = gsub("^Drug", '', drug)
  tab
})
df_signatures = do.call(cbind, df_signatures)
df_signatures = merge(df_signatures, geneInfo, by.x="row.names", by.y="ensembl_gene_id")
```

@@

```{r compare, fig.width=5, fig.height=5}
cols = c(gsub("^Drug", '',colnames(coef(fit))[-1]), 'CMCv4')

>>>>

# get and combine signatures
df_signatures = lapply( colnames(coef(fit))[-1], function(drug){
  tab = topTable(fit, coef=drug, sort.by="none", number=Inf)[,'logFC', drop=FALSE]
  colnames(tab) = gsub("^DrugExposure", '', drug)
  tab
})
df_signatures = do.call(cbind, df_signatures)
df_signatures = merge(df_signatures, geneInfo, by.x="row.names", by.y="ensembl_gene_id")
```

@@

```{r compare, fig.width=5, fig.height=5}
cols = c(gsub("^DrugExposure", '',colnames(coef(fit))[-1]), 'CMCv4')
